If the Null Fits, You Must Omit: Ubiquitous False Detections of Group Polarization

### 2025-08-13 GroupPolarizationStatmod/paper/ms.tex
combined and cleaned up software sketch and shiny app screenshot

% We begin by developing a formal model of ordinal measurement of latent
% continuous opinions (model variables and parameters are given in
% Table~\ref{tab:modelVariables}).

\begin{figure}
  \centering
    \includegraphics[width=0.8\textwidth]{Figures/Model/data-model-flow.png}
  \caption{\textbf{Workflow of the GP-stats simulation and analysis pipeline
  for estimating false detection rates under null-consistent conditions.} Colored boxes indicate file types: teal = R scripts, blue = data files, orange = plotting scripts, cyan = Slurm batch script. Arrows show the flow from parameter estimation (hillclimbing or Shiny app) to Bayesian null model fitting on the cluster, aggregation of simulated results, and final visualization.}
  \label{fig:}
\end{figure}

@@

\begin{figure}
  \caption{\textbf{Shiny web application for user-guided hillclimbing to find
  parameters that generate spurious group polarization.} This web application enables users to
create new analyses of experimental conditions from published studies. Users 
provide initial guesses for the algorithm to use as starting points in 
finding variances that generate spurious group polarization. Users inspect 
model fits provided by the algorithm, adjusting parameters if necessary, and
mark an experimental condition as ``Plausibly spurious'' if a reasonable fit
is indeed found.\mt{Maybe add some A, B, C guides to the figure and include
in parentheses here to go with the text?}}
  \centering
    \includegraphics[width=0.75\textwidth]{Figures/Model/WebApp.png}
  \label{fig:webapp}
\end{figure}

>>>>

\begin{figure}
  \centering
    % \includegraphics[width=0.8\textwidth]{Figures/Model/data-model-flow.png}
    \includegraphics[width=\textwidth]{Figures/Model/data-model-flow-w-webapp.pdf}
  \caption{\textbf{Workflow of the GP-stats simulation and analysis pipeline
  for estimating false detection rates under null-consistent conditions.} Colored boxes indicate file types: teal = R scripts, blue = data files, orange = plotting scripts, cyan
= Slurm batch script. Arrows show the flow from parameter estimation (hillclimbing or Shiny app) to Bayesian null model fitting on the cluster, aggregation of simulated results,
and final visualization. (D) shows the web app interface that takes researcher guesses at
simple consensus models that generate observations, and the app passes the guess to initialize
the hillclimbing search algorithm for finding spurious group polarization.}
  \label{fig:data-model-flow.png}
\end{figure}

@@

% \begin{figure}
%   \caption{\textbf{Shiny web application for user-guided hillclimbing to find
%   parameters that generate spurious group polarization.} This web application enables users to
% create new analyses of experimental conditions from published studies. Users 
% provide initial guesses for the algorithm to use as starting points in 
% finding variances that generate spurious group polarization. Users inspect 
% model fits provided by the algorithm, adjusting parameters if necessary, and
% mark an experimental condition as ``Plausibly spurious'' if a reasonable fit
% is indeed found.\mt{Maybe add some A, B, C guides to the figure and include
% in parentheses here to go with the text?}}
%   \centering
%     \includegraphics[width=0.75\textwidth]{Figures/Model/WebApp.png}
%   \label{fig:webapp}
% \end{figure}
